Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-06-18 ms/Thesis/thesis.tex
Add more details why it is hard to 'solve' eq12

To learn about the evolution of cooperation we investigate local stability of the equilibria of the model in \autoref{eq:nextgen_juveniles}.
The equilibria are the solutions of $\hat{p}'-\hat{p}=0$. Note that \autoref{eq:nextgen_juveniles} is not simple polynomial but a polynomial fraction, therefore the solution is not trivial.
%% DC: Yoav, I'm trying to write something like solving this is not trivial.
The fixed points (equilibria) of the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see Appendix~\ref{sec:appendixB} \autoref{eq:general_equilibrium_appendix})
\begin{equation} \label{eq:general_equilibrium}
  \hat{p}^* =  
  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
\end{equation}

>>>>

To learn about the evolution of cooperation we investigate local stability of the equilibria of the model in \autoref{eq:nextgen_juveniles}.
The equilibria are the solutions of $\hat{p}'-\hat{p}=0$. Note that \autoref{eq:nextgen_juveniles} may look simple cubic polynomial. However, because $\bar{w}$ is a function of $\hat{p}$, \autoref{eq:nextgen_juveniles} is not simple polynomial but a fractional polynomial. 
The solution of fractional polynomial is not trivial and that is why it is better to find the equilibria and analyze the stability.
The fixed points (equilibria) of the recursion (\autoref{eq:nextgen_juveniles}) are $\hat p=0$, $\hat p=1$, and (see Appendix~\ref{sec:appendixB} \autoref{eq:general_equilibrium_appendix})
\begin{equation} \label{eq:general_equilibrium}
  \hat{p}^* =  
  \frac{\alpha bvT_A - cv(1-T_B) + (T_A-T_B)}{\big[c(1-v) - b (1-\alpha v)\big] (T_A-T_B)} \;.
\end{equation}
